# Линал {#math-linal}

{{< include other/_symbols.qmd >}}

```{r opts, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, error=FALSE)
```

:::{.intro}
Вступление
:::


## Векторы {#math-linal-vectors}

## Матрицы {#math-linal-matrices}

### Особые матрицы {#math-linal-matrix-special}

#### Нулевая матрица {#math-linal-matrix-null}

$$
\vm O = \pmatrix{
0 & 0 & 0 & \cdots & 0 \\
0 & 0 & 0 & \cdots & 0 \\
0 & 0 & 0 & \cdots & 0 \\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & 0 \\
}
$$

#### Единичная матрица {#math-linal-matrix-identity}

$$
\vm I = \pmatrix{
1 & 0 & 0 & \cdots & 0 \\
0 & 1 & 0 & \cdots & 0 \\
0 & 0 & 1 & \cdots & 0 \\
\vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & \cdots & 1 \\
}
$$

### Операции над матрицами {#math-linal-matrix-operations}

#### Сложение матриц {#math-linal-matrix-sum}

* коммутативность --- $\vm A + \vm B = \vm B + \vm A$
* ассоциативность --- $(\vm A + \vm B) + \vm C = \vm A + (\vm B + \vm C)$
* $\vm A + \vm O = \vm O + \vm A = \vm A$
* $\vm A + (- \vm A) = \vm O$

#### Умножение матрицы на число {#math-linal-matrix-multiplication}

$$
\alpha \vm A = (\alpha a_{ij})
$$

* $1 \cdot \vm A = \vm A \cdot 1 = \vm A$
* $(\alpha \beta) \vm A = \alpha (\beta \vm A)$
* $(\alpha + \beta) \vm A = \alpha \vm A + \beta \vm A$
* $\alpha (\vm A + \vm B) = \alpha \vm A + \alpha \vm B$



#### Умножение матриц друг на друга {#math-linal-matrix-prod}

$$
\vm A_{m \times k} \times \vm B_{k \times n} = \vm C, c_{ij} = \sum_{l=1}^k a_{il} b_{lj}
$$

* $(\vm A \vm B) \vm C = \vm A(\vm B \vm C)$
* $\vm A \vm B \neq \vm B \vm A$
* $\vm A \vm I = \vm I \vm A = \vm A$
* $(\vm A + \vm B)\vm C = \vm A \vm C + \vm B \vm C$
* $\vm A (\vm B + \vm C) = \vm A \vm B + \vm A \vm C$
* $(\alpha \vm A) \vm B = \vm A (\alpha \vm B) + \alpha (\vm A \vm B)$

#### Транспонирование матрицы {#math-linal-matrix-transpose}

* $\tp{(\tp{\vm A})} = \vm A$
* $\tp{(\vm A \vm B)} = \tp{\vm B} \tp{\vm A}$
* $\tp{(\vm A^{-1})} = (\tp{\vm A})^{-1}$, если существует $\vm A^{-1}$
* $\tp{(\vm A + \vm B)} = \tp{\vm A} + \tp{\vm B}$
* $\det \vm A = \det \tp{\vm A}$

***

###### Session Info {#session_info .unnumbered}

```{r session-info}
sessionInfo()
```

```{=html}
<script type="text/javascript" src="./js/chapter.js"></script>
```
