# Оценивание параметров в статистическом анализе {#prob-statestim}

{{< include other/_symbols.qmd >}}

```{r opts, echo=FALSE, eval=TRUE, message=FALSE, warning=FALSE, error=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE, message=FALSE, warning=FALSE, error=FALSE)
```

:::{.intro}
Вступление
:::



## Точечные оценки {#prob-statestim-point}

:::{.lab-junior}
:::

### Получение точечных оценок {#prob-statestim-point-get}





### Свойства точечных оценок {#prob-statestim-point-props}

:::{.lab-middle}
:::

#### Несмещенность {#prob-statestim-point-props-unbiasedness}

:::{.lab-middle}
:::

$$
\forall n \, \expect \hat \theta (X_1, X_2, \ldots, X_n) = \theta
$$


#### Состоятельность {#prob-statestim-point-props-consistency}

:::{.lab-middle}
:::

$$
\forall \vepsilon > 0 \, \lim_{n \to \infty} \prob (|\hat \theta - \theta| > \vepsilon) = 0
$$



#### Эффективность {#prob-statestim-point-props-effectiveness}

:::{.lab-middle}
:::

$$
\disp \hat \theta \to \min
$$





## Интервальные оценки {#prob-statestim-interval}

:::{.lab-junior}
:::


### Стандартная ошибка {#prob-statestim-se}

:::{.lab-junior}
:::


### Доверительный интервал {#prob-statestim-ci}

:::{.lab-junior}
:::




***

###### Session Info {#session_info .unnumbered}

```{r session-info}
sessionInfo()
```

```{=html}
<script type="text/javascript" src="./js/chapter.js"></script>
```
